Meta RL analyses

### 2019-02-12 meta_RL_analyses.Rmd
Some further exploration of language resulst

```{r}
num_runs = 10
results_dir = "results/paper_results/"

result_subdirs = c("nometa",# "nometa_su_heldout", "nometa_random_holdout_longer", "nometa_only_one",  "nometa_only_one_ho",
                   "basic", #"basic_su_heldout", "basic_random_holdout_longer", "basic_only_one", "basic_only_one_ho",
                   "language")

@@

@@

```{r}
language_d = load_d(results_dir, result_subdirs, num_runs, "new_language_rewards")

@@

```{r}
summary_plot(language_d %>%
               filter(epoch == 0),
             "game_type", "reward", "is_new_game",
             simple_baselines) +
  facet_wrap(. ~ run_type)
```

@@

```{r}
meta_d = load_d(results_dir, c("basic", 
                               #"basic_su_heldout", "basic_random_holdout_longer", "basic_only_one", "basic_only_one_ho",
                               "language"), num_runs, "new_meta_true_losses")

@@

>>>>

```{r}
num_runs = 5
results_dir = "results/paper_results/"

result_subdirs = c("nometa",# "nometa_su_heldout", "nometa_random_holdout_longer", "nometa_only_one",  "nometa_only_one_ho",
                   "basic", #"basic_su_heldout", 
                   "basic_random_holdout_longer", # "basic_only_one", "basic_only_one_ho",
                   "language", "language_drop_03", "language_drop_05", "language_noncompositional")

@@

```{r}
summary_plot(reward_d %>%
               filter(epoch == 0,
                      run_type %in% c("basic", "basic_random_holdout_longer")),
             "game_type", "reward", "is_new_game",
             simple_baselines) +
  facet_wrap(. ~ run_type)
ggsave("~/Documents/grad/res/psych/ARRR/figures/meta_RL/basic_random_holdout_half.png", width=5, height=3)
```

@@

```{r}
language_d = load_d(results_dir, c("language", "language_drop_03", "language_drop_05", "language_noncompositional"), num_runs, "new_language_rewards")

@@

```{r}
ggplot(language_d %>%
         filter(epoch == 0,
                is_new_game),
       aes(x=run_type, y=reward, fill=as.factor(run))) +
  geom_hline(yintercept=0.,
             linetype=2,
             alpha=0.5) +
  geom_violin(position="dodge") +
  scale_color_brewer(palette="Set2") 
```

```{r}
summary_plot(language_d %>%
               filter(epoch == 0),
             "game_type", "reward", "is_new_game",
             simple_baselines) +
  facet_wrap(. ~ run_type)
ggsave("~/Documents/grad/res/psych/ARRR/figures/meta_RL/crappy_language.png", width=5, height=3)
```

@@

```{r}
meta_d = load_d(results_dir, c("basic", 
                               #"basic_su_heldout",
                               "basic_random_holdout_longer"# "basic_only_one", "basic_only_one_ho",
                               #"language"
                               ), num_runs, "new_meta_true_losses")

@@

```{r}
summary_plot(meta_d %>%
               filter(epoch == 0,
                      run_type %in% c("basic", "basic_random_holdout_longer")),
             "meta_task", "reward", "is_new") +
  facet_wrap(. ~ run_type)

ggsave("~/Documents/grad/res/psych/ARRR/figures/meta_RL/basic_basic_random_meta.png", width=5, height=3)
```
